Manuscript_1

### 2024-04-03 Manuscript_1.Rmd
Final edit of all main figures

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      results = "as.is", 
                      fig.height = 3, 
                      cache = TRUE, 
                      tidy = TRUE, 
                      fig.pos = "H")
```

@@

```{r load_lib, eval = FALSE, echo = TRUE}
# Load
library("tidyverse")
library("rstatix")
library("ggpubr")
library("plotgardener")
#library("BSgenome.Hsapiens.UCSC.hg38")
#library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("TxDb.Hsapiens.UCSC.hg38.refGene")
library("org.Hs.eg.db")
library("extrafont")
library("showtext")
library("JASPAR2020")
library("TFBSTools")
library("ggseqlogo")
library("biomaRt")
library("LDlinkR")
library("AllelicImbalance")
library("png")
library("AnnotationDbi")
library("scales")
library("flowCore")
library("ggcyto")

# Check
packageVersion("tidyverse") #2.0.0
packageVersion("rstatix") #0.7.2
packageVersion("ggpubr")  #0.6.0
packageVersion("plotgardener")  #1.4.2
#packageVersion("BSgenome.Hsapiens.UCSC.hg38") #1.4.5
#packageVersion("TxDb.Hsapiens.UCSC.hg38.knownGene") #3.16.0
packageVersion("TxDb.Hsapiens.UCSC.hg38.refGene") #3.15.0
packageVersion("org.Hs.eg.db")  #3.16.0
packageVersion("extrafont") #0.19
packageVersion("showtext")  #0.9.6
packageVersion("JASPAR2020")  #0.99.10
packageVersion("TFBSTools") #1.36.0
packageVersion("ggseqlogo") #0.1
packageVersion("biomaRt") #2.54.1
packageVersion("LDlinkR") #1.3.0
packageVersion("AllelicImbalance")  #1.36.0
packageVersion("png") #0.1.8
packageVersion("AnnotationDbi") #1.60.2
packageVersion("dbplyr")  #2.3.4

@@

# FIGURES
### FIGURE 1
```{r fig1, eval = FALSE, echo = TRUE}
########## FIGURE 1 ##########
##############################
# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.pdf",
    width = 8.3, 
    height = 11.7)

#### PANEL A - 
# text Figure 1
plotText(label = "Figure 1", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text B
plotText(label = "B", 
         fontsize = 12,
         x = 0.25, 
         y = 1.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text C
plotText(label = "C", 
         fontsize = 12,
         x = 0.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text D
plotText(label = "D", 
         fontsize = 12,
         x = 0.25, 
         y = 8.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

###################
#### Figure 1A ####
###################
Fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")

# Plot Figure 1A
plotRaster(image = Fig1A,
           x = 0.375,
           y = 0.625,
           width = 7.55,
           height = 1.0,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

@@

###################
#### Figure 1C ####
###################
Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")

Fig1C_tab1.1 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-1.png")
Fig1C_tab1.2 = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_SNPs_tab1.png/Fig1C_SNPs_tab1.png-2.png")

# Plot Figure 1C
plotRaster(image = Fig1C_pip,
           x = 0.375,
           y = 5.25,
           width = 3.0,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

plotRaster(image = Fig1C_tab1.1,
           x = 3.375,
           y = 5.25,
           width = 2.3,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

plotRaster(image = Fig1C_tab1.2,
           x = 5.8,
           y = 5.25,
           width = 2.3,
           height = 2.5,
           just = c("left", 
                    "top"),
           interpolate = FALSE)

#diag_edge_data = tibble(from = c("~17x10^6\nPD GWAS SNPs",
#                                 "~3400 significant\nPD GWAS SNPs",
#                                 "28 significant\nPD rSNPs"),
#                        to = c("~3400 significant\nPD GWAS SNPs",
#                               "28 significant\nPD rSNPs",
#                               "3 significant\nPD rSNPs"))
#
#diag_node_data = tibble(name = c("~17x10^6\nPD GWAS SNPs",
#                                 "~3400 significant\nPD GWAS SNPs",
#                                 "28 significant\nPD rSNPs",
#                                "3 significant\nPD rSNPs"),
#                        label = name)

# Diagramme
# fig1C = ggflowchart(diag_edge_data,
#                    diag_node_data,
#                    text_size = 3.0,
#                    arrow_size = 0.2)

# Place the diagramme
#plotGG(plot = fig1C, 
#       x = 0.5, 
#       y = 4.5, 
#      width = 1.5, 
#       height = 3.0,
#       just = c("left", "top"), 
#      default.units = "inches")

@@

# Locus plot
# Load the Nalls et al. GWAS data
nalls_allSNPs.HG38.GR = readRDS(
  "/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")

#nalls_allSNPs.HG38.GR = readRDS(
#  "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")

# Here our SNPs of interest and their location
snp = GRanges(seqnames = c("chr10", "chr4", "chr4"),
              ranges = IRanges(start = c(119651404, 987107, 76213716),
                               end = c(119651405, 987108, 76213717)))

@@

# Get SNPs info from Ensembl
snp.ensembl = useEnsembl(biomart = "snp", dataset = "hsapiens_snp")

@@

# Get rsID of SNPs that are significant and append 
position_chr10 = Nalls_sel_reg.BAG3 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

@@

# Plot
BAG3.pl = Nalls_sel_reg.BAG3 %>% 
  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
  left_join(BAG3_R2, by = "Coord") %>% 
  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x,R2) %>% 
  dplyr::rename(chrom = seqnames,
               pos = base_pair_position,
               snp = refsnp_id.x, 
               LD = R2) %>% 
  mutate(chrom = as.character(chrom)) %>% 
  group_by(LD) %>% 
  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))

@@

# Filter for the SNP in IDUA regulatory region
Nalls_sel_reg.IDUA = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  filter(seqnames == "chr4",
         between(base_pair_position, 987108 - r, 987108 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr4" & base_pair_position == 987108, "rs11248061", ""))

# Get rsID of SNPs that significant and append 
position_chr4.IDUA = Nalls_sel_reg.IDUA %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

@@

IDUA_SNPs_LD = IDUA_SNPs_LD %>% 
  filter(!str_detect(refsnp_id, "^CR"))

@@

# Filter for the SNP in SCARB2 regulatory region
Nalls_sel_reg.SCARB2 = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  filter(seqnames == "chr4",
         between(base_pair_position, 76213717 - r, 76213717 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr4" & base_pair_position == 76213717, "rs1465922", ""))

# Get rsID of SNPs that significant and append 
position_chr4.SCARB2 = Nalls_sel_reg.SCARB2 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

@@

#### PANEL A - BAG3 locus
# text Figure 2
plotText(label = "Figure 2", 
         fontsize = 14,
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")
# text A
plotText(label = "A", 
         fontsize = 12,
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# ATACseq signal BAG3
# path where bigwig files are
bw.path = "/home/vagrant/epifunc/"

@@

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         x = 0.75, 
         y = 0.875, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         x = 0.75, 
         y = 1.25, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 1.625, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 2.0, 
         just = c("left", "top"),
         default.units = "inches")

#### PANEL B - BAG3 and LHX1 expression (RNAseq)
# text B
plotText(label = "B", 
         fontsize = 12,
         x = 5.0, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

# Load it for making the plots
dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")

@@

LHX1 = as.list(LHX1)
LHX1_TFBS = ggseqlogo(LHX1)

# Place the plot
plotGG(plot = LHX1_TFBS, 
       x = 1.7125, 
       y = 2.625, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

@@

# text C
plotText(label = "C", 
         fontsize = 12,
         x = 0.25, 
         y = 4.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         x = 0.75, 
         y = 4.625, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         x = 0.75, 
         y = 5.0, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 5.375, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 5.75, 
         just = c("left", "top"),
         default.units = "inches")

#### PANEL D - IDUA and ZBTB14 expression (RNAseq)
# text D
plotText(label = "D", 
         fontsize = 12,
         x = 5.0, 
         y = 4.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

ZBTB14 = as.list(ZBTB14)
ZBTB14_TFBS = ggseqlogo(ZBTB14)

# Place the plot
plotGG(plot = ZBTB14_TFBS, 
       x = 1.7125, 
       y = 6.625, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

# text E
plotText(label = "E", 
         fontsize = 12,
         x = 0.25, 
         y = 8.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         x = 0.75, 
         y = 8.375, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         x = 0.75, 
         y = 8.75, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 9.125, 
         just = c("left", "top"),
         default.units = "inches")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 9.5, 
         just = c("left", "top"),
         default.units = "inches")

# text F
plotText(label = "F", 
         fontsize = 12,
         x = 5.0, 
         y = 8.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

NR2C2 = as.list(NR2C2)
NR2C2_TFBS = ggseqlogo(NR2C2)

# Place the plot
plotGG(plot = NR2C2_TFBS, 
       x = 1.6875, 
       y = 10.375, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

@@

# Save as TIFF, 300 dpi
tiff("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.tiff",
     width = 8.27,
     height = 11.67,
     units = "in",
     res = 300)

@@

```{r}
sessionInfo()
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      results = "as.is", 
                      fig.height = 3, 
                      cache = FALSE, 
                      tidy = TRUE, 
                      fig.pos = "H")
```

@@

```{r load_lib, eval = FALSE, echo = TRUE}
# Load
library("tidyverse")
library("rstatix")
library("ggpubr")
library("plotgardener")
#library("BSgenome.Hsapiens.UCSC.hg38")
library("TxDb.Hsapiens.UCSC.hg38.knownGene")
library("TxDb.Hsapiens.UCSC.hg38.refGene")
library("org.Hs.eg.db")
library("extrafont")
library("showtext")
library("JASPAR2020")
library("TFBSTools")
library("ggseqlogo")
library("biomaRt")
library("LDlinkR")
library("AllelicImbalance")
library("png")
library("AnnotationDbi")
library("scales")
library("flowCore")
library("ggcyto")
library("ggmanh")

# Check
packageVersion("tidyverse") #2.0.0
packageVersion("rstatix") #0.7.2
packageVersion("ggpubr")  #0.6.0
packageVersion("plotgardener")  #1.4.2
#packageVersion("BSgenome.Hsapiens.UCSC.hg38") #1.4.5
#packageVersion("TxDb.Hsapiens.UCSC.hg38.knownGene") #3.16.0
packageVersion("TxDb.Hsapiens.UCSC.hg38.refGene") #3.15.0
packageVersion("org.Hs.eg.db")  #3.16.0
packageVersion("extrafont") #0.19
packageVersion("showtext")  #0.9.6
packageVersion("JASPAR2020")  #0.99.10
packageVersion("TFBSTools") #1.36.0
packageVersion("ggseqlogo") #0.1
packageVersion("biomaRt") #2.54.1
packageVersion("LDlinkR") #1.3.0
packageVersion("AllelicImbalance")  #1.36.0
packageVersion("png") #0.1.8
packageVersion("AnnotationDbi") #1.60.2
packageVersion("dbplyr")  #2.3.4
packageVersion("ggmanh")  #1.2.0

@@

# FIGURES
Generating the manhattan plot for the PD GWAS is memory demanding. Go to the HPC
```{bash, eval = FALSE, echo = TRUE}
ssh iris-cluster
salloc --nodes=1 -p interactive --qos debug -C batch -t 02:00:00 --mem 24G

# Load the Singularity module
module load tools/Singularity/3.8.1
singularity shell --bind /scratch/users/dgerard:/scratch/users/dgerard $HOME/Singularity_containers/Manuscript_1_singularity.sif
```

### FIGURE 1
```{r fig1, eval = FALSE, echo = TRUE}
########## FIGURE 1 ##########
##############################
# Save as a PDF
pdf("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.pdf",
    width = 8.3, 
    height = 11.7)

# Save as TIFF, 300 ppi
tiff("/home/vagrant/Manuscript_1/FIGURE1/FIGURE1.tiff",
     width = 8.27,
     height = 11.67,
     units = "in",
     res = 300,
     compression = "lzw")

# Create a A4 blank page
pageCreate(width = 8.27, 
           height = 11.67, 
           default.units = "inches",
           showGuides = FALSE)

#### PANEL A - 
# text Figure 1
plotText(label = "Figure 1", 
         fontsize = 14,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text A
plotText(label = "A", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

###################
#### Figure 1A ####
###################
# Figure 1A generated in Biorender
#fig1A = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Fig1A.png")
fig1A = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1A.png")

plotRaster(image = fig1A,
           x = 0.25, 
           y = 1, 
           width = 8.0, 
           height = 1.0, 
           just = "left",
           interpolate = TRUE)

# text B
plotText(label = "B", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 1.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text C
plotText(label = "C", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text D
plotText(label = "D", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 3.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text E
plotText(label = "E", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 4.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

###################
#### Figure 1C ####
###################
Fig1C_pip = readPNG("/home/vagrant/Manuscript_1/FIGURE1/Fig1C_pipeline.png")
#Fig1C_pip = readPNG("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Fig1C_pipeline.png")

# Plot Figure 1C - Pipeline
plotRaster(image = Fig1C_pip,
           x = 0.375,
           y = 4.75,
           width = 3.0,
           height = 3.5,
           just = c("left", 
                    "top"),
           interpolate = TRUE)

###################
#### Figure 1C Manhattan plot ####
###################
# Load the Nalls et al. GWAS data
nalls_allSNPs.HG38.GR = readRDS(
  "/home/vagrant/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")

#nalls_allSNPs.HG38.GR = readRDS(
#"/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/nalls_allSNPs.HG38.GR.rds")

# Load the rsIDS FOR THE 28 significant SNPs
rsID.28 = read_delim("/home/vagrant/Manuscript_1/FIGURE1/20210309_28SNPs_rsID.csv",
                     delim = ",",
                     col_names = TRUE)

rsID.28 = read_delim("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20210309_28SNPs_rsID.csv",
                     delim = ",",
                     col_names = TRUE)

rsID.28.filt = rsID.28 %>% 
  dplyr::select(chrom, chromEnd, name) %>% 
  unite(col = "pos", chrom, chromEnd, sep = "_")

# Select the SNPs position from nalls et al and associate rsIDs
nalls.manH = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  dplyr::select(seqnames, base_pair_position, p) %>% 
  unite(col = "pos", seqnames, base_pair_position, sep = "_", remove = FALSE) %>%
  left_join(rsID.28.filt, by = "pos") %>% 
  separate(pos, into = c("chrom", "pos"), sep = "_", remove = TRUE) %>% 
  dplyr::select(chrom, pos, p, name)

# Save
write_rds(nalls.manH,
          "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")

nalls.manH = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")
nalls.manH = read_rds("/home/vagrant/Manuscript_1/FIGURE1/20240304_28SNPs_rdID_manH.rds")

# Rename columns
nalls.manH = nalls.manH %>% 
  dplyr::rename(snp = name) %>% 
  mutate(pos = as.numeric(pos)) %>% 
  dplyr::filter(chrom %in% rsID.28$chrom)

# Manhattan plot - highlight  the 28 SNPs with rsID
snp_2_high = nalls.manH %>% 
  dplyr::filter(!is.na(snp),
                p <= 5e-08)

# Random sampling for plotting test
snp_to_pl = nalls.manH %>% 
  mutate(snp = NA_character_) %>% 
  bind_rows(snp_2_high) %>% 
  #dplyr::filter(p <= 5e-08) %>% 
  mutate(pbis = -log10(p),
         chrom = factor(chrom,
                        levels = c("chr1",
                                   "chr3",
                                   "chr4",
                                   "chr7",
                                   "chr10",
                                   "chr12",
                                   "chr16",
                                   "chr17")))

# And plot
snp.pl = manhattan_plot(x = snp_to_pl, 
               pval.colname = "p", 
               chr.colname = "chrom", 
               pos.colname = "pos",
               label.colname = "snp",
               signif = 5e-08,
               max.overlaps = 50)

saveRDS(snp.pl,
        "/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE1/Nalls_manh_label.rds")
snp.pl = readRDS("/home/vagrant/Manuscript_1/FIGURE1/Nalls_manh_label.rds")

# Place the plot
plotGG(plot = snp.pl, 
       x = 3.5, 
       y = 4.75, 
       width = 4.5, 
       height = 3.5,
       just = c("left", "top"), 
       default.units = "inches")

@@

# Locus plot
# Here our SNPs of interest and their location
snp = GRanges(seqnames = c("chr10", "chr4", "chr4"),
              ranges = IRanges(start = c(119651404, 987107, 76213716),
                               end = c(119651405, 987108, 76213717)))

@@

# Get SNPs info from Ensembl
#snp.ensembl = useEnsembl(biomart = "snp", 
#                         dataset = "hsapiens_snp")

snp.ensembl = useMart(biomart = "ENSEMBL_MART_SNP",
                      dataset = "hsapiens_snp")

@@

# Get rsID of SNPs that are significant and append 
position_chr10 = Nalls_sel_reg.BAG3 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  dplyr::filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

@@

# Plot
BAG3.pl = Nalls_sel_reg.BAG3 %>% 
  unite("Coord", seqnames, base_pair_position, sep = ":", remove = FALSE) %>% 
  left_join(BAG3_R2, by = "Coord") %>% 
  dplyr::select(seqnames, base_pair_position, p, refsnp_id.x, R2) %>% 
  dplyr::rename(chrom = seqnames,
               pos = base_pair_position,
               snp = refsnp_id.x, 
               LD = R2) %>% 
  mutate(chrom = as.character(chrom)) %>% 
  group_by(LD) %>% 
  mutate(LD_grp = cut(LD, seq(0, 1.0, 0.2)))

@@

# Filter for the SNP in IDUA regulatory region
Nalls_sel_reg.IDUA = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  dplyr::filter(seqnames == "chr4",
         between(base_pair_position, 987108 - r, 987108 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr4" & base_pair_position == 987108, "rs11248061", ""))

# Get rsID of SNPs that significant and append 
position_chr4.IDUA = Nalls_sel_reg.IDUA %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  dplyr::filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

@@

IDUA_SNPs_LD = IDUA_SNPs_LD %>% 
  dplyr::filter(!str_detect(refsnp_id, "^CR"))

@@

# Filter for the SNP in SCARB2 regulatory region
Nalls_sel_reg.SCARB2 = nalls_allSNPs.HG38.GR %>% 
  as_tibble() %>% 
  dplyr::filter(seqnames == "chr4",
         between(base_pair_position, 76213717 - r, 76213717 + r)) %>% 
  mutate(minus_log_10_p = -log10(p),
         GWAS_p_sig = if_else(minus_log_10_p > -log10(5e-8), "yes", "no"),
         rsID = if_else(seqnames == "chr4" & base_pair_position == 76213717, "rs1465922", ""))

# Get rsID of SNPs that significant and append 
position_chr4.SCARB2 = Nalls_sel_reg.SCARB2 %>% 
  mutate(chr = gsub("chr", "", seqnames)) %>% 
  unite(col = "position", c(chr, end, base_pair_position), sep = ":", remove = FALSE) %>% 
  dplyr::filter(GWAS_p_sig != "no") %>%
  dplyr::select(position) %>% 
  pull()

@@

# Save as TIFF, 300 ppi
tiff("/home/vagrant/Manuscript_1/FIGURE2/FIGURE2.tiff",
     width = 8.27,
     height = 11.67,
     units = "in",
     res = 300,
     compression = "lzw")

# Create a A4 blank page
pageCreate(width = 8.27, 
           height = 11.67, 
           default.units = "inches",
           showGuides = FALSE)

#### PANEL A - BAG3 locus
# text Figure 2
plotText(label = "Figure 2", 
         fontsize = 14,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# text A
plotText(label = "A", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

# ATACseq signal BAG3
# path where bigwig files are
bw.path = "/home/vagrant/epifunc/"
#bw.path = "/Volumes/deborah.gerard/Documents/epifunc/"

@@

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 0.875, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontfamily = "Helvetica",
         fontcolor = "#B22222",
         x = 0.75, 
         y = 1.25, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontfamily = "Helvetica",
         fontcolor = "#DC143C",
         x = 0.75, 
         y = 1.625, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontfamily = "Helvetica",
         fontcolor = "#E9967A",
         x = 0.75, 
         y = 2.0, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

#### PANEL B - BAG3 and LHX1 expression (RNAseq)
# text B
plotText(label = "B", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 5.0, 
         y = 0.5, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

# Load it for making the plots
dat.RPKM.filt = read_rds("/home/vagrant/Manuscript_1/FIGURE2/mat_RPKM.rds")
dat.RPKM.filt = read_rds("/Volumes/deborah.gerard/Documents/Manuscript_1/FIGURE2/mat_RPKM.rds")

dat.RPKM.filt %>% 
  #filter(str_detect(gene_id, " ENSG00000272414"))
  filter(str_detect(gene_name, paste0(c("FAM47E", "STBD1"),
                                      collapse = "|"))) %>% 
  View()

@@

LHX1 = as.list(LHX1)

# Remove the nucleotide position
LHX1_TFBS = ggseqlogo(LHX1) +
  annotate("rect", 
           xmin = 4.5, 
           xmax = 5.5, 
           ymin = -0.05, 
           ymax = 2.5, 
           alpha = .1, 
           col = "black", 
           fill = "#404788FF") +
  theme(axis.text.x = element_blank())

# Place the plot
plotGG(plot = LHX1_TFBS, 
       x = 1.7425, 
       y = 2.625, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

@@

# text C
plotText(label = "C", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 4.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 4.625, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 5.0, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 5.375, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 5.75, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

#### PANEL D - IDUA and ZBTB14 expression (RNAseq)
# text D
plotText(label = "D", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 5.0, 
         y = 4.25, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

ZBTB14 = as.list(ZBTB14)

# Remove the nucleotide position
ZBTB14_TFBS = ggseqlogo(ZBTB14) +
  annotate("rect", 
           xmin = 8.5, 
           xmax = 9.5, 
           ymin = -0.05, 
           ymax = 2.5, 
           alpha = .1, 
           col = "black", 
           fill = "#404788FF") +
  theme(axis.text.x = element_blank())

# Place the plot
plotGG(plot = ZBTB14_TFBS, 
       x = 1.6225, 
       y = 6.625, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

# text E
plotText(label = "E", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 0.25, 
         y = 8.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

# Add the samples name
plotText(label = "smNPC", 
         fontsize = 6, 
         fontcolor = "#A9A9A9",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 8.375, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D15", 
         fontsize = 6, 
         fontcolor = "#B22222",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 8.75, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D30", 
         fontsize = 6, 
         fontcolor = "#DC143C",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 9.125, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

plotText(label = "mDAN D50", 
         fontsize = 6, 
         fontcolor = "#E9967A",
         fontfamily = "Helvetica",
         x = 0.75, 
         y = 9.5, 
         just = c("left", "top"),
         default.units = "inches",
         fontface = "bold")

# text F
plotText(label = "F", 
         fontsize = 12,
         fontfamily = "Helvetica",
         x = 5.0, 
         y = 8.0, 
         just = "left", 
         default.units = "inches",
         fontface = "bold")

@@

NR2C2 = as.list(NR2C2)

# Remove nucleotide
NR2C2_TFBS = ggseqlogo(NR2C2) +
  annotate("rect", 
           xmin = 3.5, 
           xmax = 4.5, 
           ymin = -0.05, 
           ymax = 2.0, 
           alpha = .1, 
           col = "black", 
           fill = "#404788FF") +
  theme(axis.text.x = element_blank())

# Place the plot
plotGG(plot = NR2C2_TFBS, 
       x = 1.8475, 
       y = 10.375, 
       width = 1.5, 
       height = 1.5,
       just = c("left", "top"), 
       default.units = "inches")

@@

# Save as TIFF, 300 dpi
tiff("/home/vagrant/Manuscript_1/FIGURE3/FIGURE3.tiff",
     width = 8.27,
     height = 11.67,
     units = "in",
     res = 300,
     compression = "lzw")

# Create a A4 blank page
pageCreate(width = 8.27, 
           height = 11.67, 
           default.units = "inches",
           showGuides = FALSE)

@@

```{r, eval = FALSE, echo = TRUE}
sessionInfo()
```
